Ultra Diffuse Galaxies associated with Milky-Way Analogs

### 2022-08-22 main.tex
Updates from Overleaf

@@

@@

\subsubsection{Completeness}\label{sec:completeness}

@@

\begin{figure*}
	\vbox{ 
		%\vskip -10mm
		\centering
		\includegraphics[width=1\linewidth]{completeness.pdf}
	}
	\caption{The completeness of our LSBG search as a function of effective radius $r_e$ and the average surface brightness $\sbeff$. We characterize the completeness by injecting mock \sersic{} galaxies into coadd images. The overall completeness (right panel) comprises the detection completeness (left panel, see Sec. \ref{sec:detection}) and deblending completeness (middle panel, see Sec. \ref{sec:deblending}) where false positives are removed. The dashed lines in the right panel highlight the 70\%, 50\%, and 20\% completeness contours. The completeness drops for smaller sizes and faint surface brightness. We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$. The completeness drops as we go to fainter surface brightness and smaller size. 
	%The mock galaxies span a large range in size, surface brightness, \sersic{} index, color, and ellipticity. 
	}
	\label{fig:completeness}
\end{figure*}

@@

Similar to \citet{Zaritsky2021}, we model the bias and uncertainty in size, surface brightness, total magnitude, and color as a function of other parameters including size, surface brightness, and shapes. However, we do not find any significant dependence of the bias on color, ellipticity, and Spergel index. Thus we just model the bias and uncertainty as a function of angular size $r_e$ and surface brightness $\sbeff$.

We split the $r_e-\overline{\mu}_{\rm eff}(g)$ plane using an $8\times 8$ grid, and calculate the mean bias within each bin. Then we interpolate over the grid using a multiquadratic kernel\footnote{\url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.interpolate.RBFInterpolator.html}}. Figure \ref{fig:meas_err} shows the interpolated bias terms as a function of the measured size and surface brightness. For half-light radius, we take $(r_{e, \rm t} - r_{e, \rm m}) / r_{e,\rm m}$ as the bias term; for surface brightness, we take $\overline{\mu}_{\rm eff, t}(g) - \overline{\mu}_{\rm eff, m}(g)$ as the bias term. As shown in Figure \ref{fig:meas_err}, the size and surface brightness bias grows with increasing surface brightness. The bias has a peak at $r_e\sim 6\arcsec$ because the $r_e$ shown in the figure is the measured size, not the true size. It is the bias in size measurement that makes galaxies with large intrinsic $r_e$ pile up around $r_e\sim 6\arcsec$. We also find that the bias in $g-i$ color is quite small.

For LSBGs in our sample, we apply corrections for the bias using the interpolated bias terms. We first correct for the bias in size, $g$-band average surface brightness, $g-r$ and $g-i$ colors. Then we calculate the $g$-band apparent magnitude following $m_g = \overline{\mu}_{\rm eff}(g) - 2.5\log(2\pi r_e^2)$. The magnitudes and surface brightnesses in other bands are derived using $g$-band magnitude, surface brightness, and colors. In this way, we apply a self-consistent correction for the measurement bias to the data.

It is also important to characterize the measurement uncertainty. The measurement uncertainty consists of a statistical uncertainty which is determined by the shape of the likelihood (posterior) surface, and a systematic uncertainty which is related to various factors including sky subtraction, contamination effects, etc. Unlike other parametric modeling codes such as \code{galfit} or \code{imfit}, \code{scarlet} does not explore the full likelihood (posterior) space but rather finds one optimal solution. Thus we cannot get a statistical error on the measured properties from \code{scarlet}. However, by comparing the recovered properties of mock galaxies with the truth, we can empirically estimate the measurement uncertainty without knowing the impact of each factor. Following the same method as that of calculating the bias, in each bin we compute the standard deviation of the difference between the truth and the bias-corrected measurement, then we interpolate over the grid. The measurement errors are shown in Figure \ref{fig:meas_err} as contours.

Overall, the measurement agrees with the truth quite well. However, the size and the total flux of galaxies below $\overline{\mu}_{\rm eff} (g) > 27\ \sbunit$ are systematically under-estimated. We also characterize the bias and the scatter in the measurement as a function of size and surface brightness. We apply the bias correction to the LSBG measurement, and incorporate the measurement error into the science figures.

Unlike \citet{Zaritsky2021}, since we only work on a 2-D plane, we find interpolation working well enough and do not use polynomial fitting to avoid meaningless results outside of the fitting range.

We remind the readers that the values presented in our catalog are already bias-corrected. But we do provide the bias values for reference.

% Bias corrections are applied to our catalog entries before estimating their completeness probabilities.

%All satellite photometry is in the AB system and cor- rected for MW dust extinction using the E(B − V ) maps of Schlegel et al. (1998) recalibrated by Schlafly & Finkbeiner (2011). We take the solar g-band magni- tude to be Mg⊙ = 5.03 mag (Willmer 2018).

TBD: re-think the way of computing the error, especially for $r_e$.

vdB 16 doesn't consider whether GALFIT gives the corrrect $R_e$, when deriving the completeness (recovered fraction)

say somewhere in the results section that only SMUDGES measured and corrected measurement bias.

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{meas_bias.pdf}
	}
    \caption{Caption}
    \label{fig:meas_bias}
\end{figure*}

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{meas_error_spergel.pdf}
	}
    \caption{Caption}
    \label{fig:meas_err}
\end{figure*}

@@

Distance information of LSBGs is hard to know \citep{Kadowaki2021,Greene2022,Zaritsky2022} (also another cross-correlation paper recently?)

The goal of this paper is to study the UDG population hosted by MW-like galaxies. However, the properties of the MW itself vary in the literature \citep{Licquia2015,Bland-Hawthorn2016}, and the definitions of MW analogs are also different among groups. In the SAGA survey \citep{SAGA-I,SAGA-II}, MW analogs are selected based on their absolute $K$-band magnitude $-23 > M_K > -24.6$, which is derived using abundance matching by assuming a simple galaxy-halo connection model (Fig 2 of \citealt{SAGA-I}). This luminosity range approximately corresponds to a stellar mass range of $10.2 < \log\, M_\star/M_\odot < 11.0$. They also require the MW analogs to be in isolation (without nearby bright galaxies) and lie in a redshift range of $0.005 < z < 0.01$ (20-40 Mpc). In the ELVES survey \citep{ELVES-I,ELVES-II,CarlstenELVES2022}, the requirements for MW-like host is loosened to be $M_K < -22.1$~mag ($M_\star > 10^{9.9}\ M_\odot$) because the probed volume by ELVES ($D<12$ Mpc) is smaller than that of SAGA. We choose the stellar mass range of MW analogs to be $10.2 < \log\, M_\star/M_\odot < 11.2$, which is simply a 1 dex bin centered at the measured stellar mass of the Milky Way ($\sim 10^{10.7}\ M_\odot$, \citealt{Licquia2015}). MW analogs selected using this definition are very close to those in SAGA but are slightly more massive than the ELVES hosts.

Since UDGs are relatively scarce in MW-like hosts \citep{SAGA-II,CarlstenELVES2022}, it is helpful to probe a larger volume to obtain good statistics. However, UDGs will be too small and faint to be detected in HSC images beyond a certain distance. We choose our redshift range to be $0.01 < z < 0.04$, which makes sure that we can detect a significant number of faint dwarf galaxies around MW-like hosts. We exclude galaxies $z<0.01$ because 1) the number is very small; 2) their large angular size makes they may be shredded in the deblending step, so that including them will introduce a number of spurious LSB objects. Our MW analogs sample complements the ELVES sample and SAGA sample in our redshift range.

After applying the stellar mass and redshift cuts to the NSA catalog, there are 23,218 galaxies left. Then we match them to the LSBG catalog (described in Section \ref{sec:detection}) as follows. For a given MW-like host, we first calculate its virial radius $R_{\rm vir}$ assuming the stellar mass-halo mass relation in \citet{Behroozi2010}. It turns out that 40\% of hosts have virial radii larger than 300 kpc. Then we identify any LSBG that falls into the projected angular virial radius of the host. If one LSBG is matched to multiple hosts, we assign it to the nearest host based on the separation normalized by host virial radius. Finally, we have 901 MW-like hosts and 10,579 LSBG candidates associated with them. However, there are still a significant fraction of spurious objects in this LSBG sample, including galactic cirrus, tidal tails/streams, shredded large galaxies, compact sources in galaxy outskirts, etc. As introduced in Section \ref{sec:deblending}, we perform a deblending step to effectively remove these spurious objects. There are 2,673 objects left after the deblending cuts. Next, we model them using the Spergel profile as described in Section \ref{sec:modeling}. Based on the modeling results, we apply the same color cuts as in Section \ref{sec:deblending} and a size cut of $1.6\arcsec < r_e < 15\arcsec$ to further remove unreliable fits and false positives. We also remove duplicated objects. In the end, we have 2510 LSBG candidates as our final LSBG sample, from which we construct the ultra-diffuse galaxy (UDG) sample and the ultra-puffy galaxy (UPG) samples as follows.

@@

The measured central surface brightness might be biased by nuclear star clusters \citep{Neumayer2020} or other contaminants. Therefore in this work, we use the average surface brightness within an effective radius $\sbeff$ to define UDG. The difference between the average surface brightness and the central surface brightness for a \sersic{} profile can be analytically calculated, where $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1.124$ for $n=1$ and 0.796 for $n=0.8$ \citep{Graham2005,Yagi2016}. Since dwarf galaxies and UDGs typically show a range of \sersic{} index $0.8 < n < 1.2$ \citep{vanDokkum2015,ELVES-I}, we take $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1$ as an average value. In this work, we define UDGs to be galaxies with $r_e+\sigma(r_e) > 1.5$ kpc and $\sbeff + \sigma(\sbeff) > 25\ \sbunit$, which takes the measurement errors into account. This definition maximizes the consistency with the definition in \citet{vanDokkum2015} while not losing UDGs harboring nuclear star clusters.

@@

The concept of UDG was proposed for those dwarf galaxies with large physical size and diffuse light distribution. However, the size of a galaxy is strongly correlated with its mass, known as the mass-size relation \citep[e.g.,][]{Lange2015}. The slope of the mass-size relation has been shown to be color-dependent for galaxies above $M_\star > 10^{8.5}\ M_\odot$: blue star-forming galaxies have a shallower slope, whereas red quenched galaxies have a steeper slope. However, recent works show that the mass-size relation in the dwarf galaxy regime ($10^{5.5} < M_\star < 10^{8.5}$) is quite universal: the slope and intercept are not sensitive to the color and morphology of dwarf galaxy \citep{ELVES-I}. This gives us a chance to define a subset of dwarf galaxies that are outliers on the mass-size plane. Taking the measured mass-size relation from \citet{ELVES-I} $\log\, (r_e/\mathrm{pc}) = 0.247\, \log\, (M_\star/M_\odot) + 1.071$ and a scatter of $\sigma=0.181$ dex, we define a population of ultra-puffy galaxies (UPGs) to be galaxies that are $>1.5\sigma$ above the mass-size relation. The UPGs are not necessarily large in physical size or faint in average surface brightness {\bf JEG: but they are size outliers for their mass}. Both UDG and UPG represent subsets of dwarf galaxies that are larger and more diffuse than average. However, the hard cut on size (1.5 kpc) means that the UDG definition excludes ``large'' galaxies at the low-mass end because as mass goes smaller, the average size also gets smaller. The surface brightness cut also biases the UDG sample because of mass-to-light ratio differences between blue and red galaxies, as will be discussed in Section \ref{sec:quench}. The definition of UPG based on the observed mass-size relation is more physically-motivated, and UPGs better represent a homogeneous subset of dwarf galaxies along the stellar mass axis. There is also no color preference in the UPG definition for a given stellar mass. It is worth noting that a definition based on the mass-size relation was already used in simulation studies where simulations cannot reproduce the observed mass-size relation \citep[e.g.,][]{Benavides2021}.

@@

>>>>

Distance information of LSBGs is hard to know \citep{Kadowaki2021,Greene2022,Zaritsky2022} (also another cross-correlation paper recently?). Thus we turn to match with MW analogs.

explain those acronyms (SAGA, ELVES)

@@

\textbf{
Based on the modeling results, we apply the same color cuts as in Section \ref{sec:deblending} and a size cut of $1.6\arcsec < r_e < 15\arcsec$ to further remove unreliable fits and false positives. }
\jiaxuan{Check if this is considered in the completeness.}

@@

\subsubsection{Completeness}\label{sec:completeness}
\begin{figure*}
	\vbox{ 
		%\vskip -10mm
		\centering
		\includegraphics[width=1\linewidth]{completeness.pdf}
	}
	\caption{The completeness of our LSBG search as a function of effective radius $r_e$ and the average surface brightness $\sbeff$. We characterize the completeness by injecting mock \sersic{} galaxies into coadd images. The overall completeness (right panel) comprises the detection completeness (left panel, see Sec. \ref{sec:detection}) and deblending completeness (middle panel, see Sec. \ref{sec:deblending}) where false positives are removed. The dashed lines in the right panel highlight the 70\%, 50\%, and 20\% completeness contours. The completeness drops for smaller sizes and faint surface brightness. We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$. The completeness drops as we go to fainter surface brightness and smaller size. 
	%The mock galaxies span a large range in size, surface brightness, \sersic{} index, color, and ellipticity. 
	}
	\label{fig:completeness}
\end{figure*}

@@

@@

Similar to \citet{Zaritsky2021}, we model the bias and uncertainty in size, surface brightness, total magnitude, and color as a function of other parameters including size, surface brightness, and shapes. However, we do not find any significant dependence of the bias on color, ellipticity, and Spergel index. Thus we just model the bias and uncertainty as a function of the \textit{measured} angular size $r_e$ and surface brightness $\sbeff$.

Given the size and surface brightness of our simulated galaxies, we set the ranges of the observed size and surface brightness to be $r_e\in[1\arcsec, 15\arcsec],\ \sbeff\in[23, 29]$. We then split the observed $r_e-\overline{\mu}_{\rm eff}(g)$ plane using an $8\times 8$ grid, and calculate the mean bias $\Delta X = X_{\rm truth} - X_{\rm meas}$ within each bin, where $X=\{\sbeff,\ g-i,\ g-r\}$. For $r_e$, we calculate the relative bias $\Delta r_e / r_e$ instead because it is less dependent on the angular size. Then we interpolate over the grid using a multi-quadratic kernel\footnote{\url{https://docs.scipy.org/doc/scipy/reference/generated/scipy.interpolate.RBFInterpolator.html}}. Unlike \citet{Zaritsky2021} where they fit models in 4-D space, we find interpolation working well enough in the 2-D space and do not use polynomial fitting to avoid meaningless results outside of the fitting range. We emphasize that the bias and uncertainty are modeled to be functions of the measured properties, not intrinsic ones, such that we can correct for bias based on our measurements.

In Figure \ref{fig:meas_err}, the colors show the interpolated bias terms as a function of the measured size and surface brightness. The size and surface brightness bias grows with increasing surface brightness. The bias term is not a monotonic function of size because the size here is not intrinsic size. It is the bias in size measurement that makes galaxies with large intrinsic $r_e$ pile up around $r_e\sim 6\arcsec$. We also find the bias in $g-i$ color quite small.

For LSBGs in our sample, we apply corrections for the bias using the interpolated bias terms. We first correct for the bias in size, $g$-band average surface brightness, $g-r$ and $g-i$ colors. Then we calculate the $g$-band total magnitude following $m_g = \overline{\mu}_{\rm eff}(g) - 2.5\log(2\pi r_e^2)$. The magnitudes and surface brightnesses in other bands are derived using $g$-band magnitude, surface brightness, and colors. In this way, we apply a self-consistent correction for the measurement biases to the data.

The measurement uncertainty consists of a statistical uncertainty which is determined by the shape of the likelihood (posterior) surface, and a systematic uncertainty which is related to various factors including sky subtraction, neighboring contamination, etc. Unlike other parametric modeling codes, \code{scarlet} does not explore the full posterior space but rather finds one optimal solution. Thus we have no access to the statistical error on the measured properties from \code{scarlet}. Fortunately, by comparing the recovered properties of mock galaxies with the truth, we can empirically estimate the measurement uncertainty without knowing the impact of each factor. Following the same method as that of calculating the bias, in each bin we compute the $1\sigma$ standard deviation of the difference between the truth and the bias-corrected measurement, then we interpolate over the grid. The measurement errors $\sigma(X)$ are shown in Figure \ref{fig:meas_err} as contours, and they have the same units as the biases. We set minimum uncertainties to be $\sigma(r_e) \geqslant 0.3,\ \sigma(\overline{\mu}_{\rm eff}) \geqslant 0.05,\ \sigma(g-i) \geqslant 0.05$ to avoid meaningless uncertainty due to small statistics.

In the following sections, we apply the bias corrections to the real LSBGs, estimate the measurement uncertainties, and evaluate the completeness based on bias-corrected properties. We also incorporate the measurement errors into the science figures. The values presented in our catalogs are already bias-corrected, but we do provide the bias values for reference.

%All satellite photometry is in the AB system and cor- rected for MW dust extinction using the E(B − V ) maps of Schlegel et al. (1998) recalibrated by Schlafly & Finkbeiner (2011). We take the solar g-band magni- tude to be Mg⊙ = 5.03 mag (Willmer 2018).
% say somewhere in the results section that only SMUDGES measured and corrected measurement bias. vdB 16 doesn't consider whether GALFIT gives the corrrect $R_e$

% \begin{figure*}
% 	\vbox{ 
% 		\centering
% 		\includegraphics[width=1\linewidth]{meas_bias.pdf}
% 	}
%     \caption{Caption}
%     \label{fig:meas_bias}
% \end{figure*}

\begin{figure*}
	\vbox{ 
		\centering
		\includegraphics[width=1\linewidth]{meas_error_spergel.pdf}
	}
    \caption{The measurement bias and uncertainty as a function of measured angular size $r_e$ and surface brightness $\sbeff$. The colors show the bias term while the dashed contours show the constant uncertainty lines. We derive the bias of total magnitudes from the biases of $r_e$, $\sbeff$, and colors consistently. We find that the bias and uncertainty of our measurement increase toward the fainter end. We apply the bias correction to the real LSBGs before studying their physical properties.}
    \label{fig:meas_err}
\end{figure*}

@@

The goal of this paper is to study the UDG population hosted by MW-like galaxies. However, the properties of the MW itself vary in the literature \citep{Licquia2015,Bland-Hawthorn2016}, and the definitions of MW analogs are also different among different studies. In the SAGA survey \citep{SAGA-I,SAGA-II}, MW analogs are selected based on their absolute $K$-band magnitude $-23 > M_K > -24.6$, which is derived using abundance matching by assuming a simple galaxy-halo connection model (Fig 2 of \citealt{SAGA-I}). This luminosity range approximately corresponds to a stellar mass range of $10.2 < \log\, M_\star/M_\odot < 11.0$. They also require the MW analogs to be in isolation (without nearby bright galaxies) and lie in a redshift range of $0.005 < z < 0.01$ (20--40 Mpc). In the ELVES survey \citep{ELVES-I,ELVES-II,CarlstenELVES2022}, the requirements for MW-like host is loosened to be $M_K < -22.1$~mag ($M_\star > 10^{9.9}\ M_\odot$) because the probed volume by ELVES ($D<12$ Mpc) is smaller than that of SAGA. In this work, we choose the stellar mass range of MW analogs to be $10.2 < \log\, M_\star/M_\odot < 11.2$, which is simply a 1 dex bin centered at the measured stellar mass of the Milky Way ($\sim 10^{10.7}\ M_\odot$, \citealt{Licquia2015}). MW analogs selected using this definition are very close to those in SAGA but are slightly less massive than the ELVES hosts since ELVES has several groups more massive than SAGA.

Since UDGs are relatively scarce in MW-like hosts \citep{SAGA-II,CarlstenELVES2022}, it is helpful to probe a larger volume to obtain good statistics. However, UDGs will be too small and too faint to be detected in HSC images beyond a certain distance. We choose our redshift range to be $0.01 < z < 0.04$, which makes sure that we can detect a significant number of faint dwarf galaxies around MW-like hosts. We exclude galaxies $z<0.01$ because 1) the number of UDGs will be very small due to the small volume; 2) their large angular size makes them more probable to be shredded in the deblending step, so including them will introduce a number of spurious LSB objects. Our MW analogs sample complements the ELVES sample and SAGA sample in our redshift range.

After applying the stellar mass and redshift cuts to the NSA catalog, there are 23,218 galaxies left. Then we match them to the initial LSBG sample (described in Section \ref{sec:detection}, before the deblending step) as follows. For a given MW analog, we first calculate its virial radius $R_{\rm vir}$ assuming the stellar mass-halo mass relation in \citet{Behroozi2010}. It turns out that 40\% of hosts have virial radii larger than 300 kpc, which is commonly used as the virial radius of MW. Then we identify any LSBG that falls into the projected angular virial radius of the host. If one LSBG is matched to multiple hosts, we assign it to the nearest host based on the separation normalized by host virial radius. Finally, we have 901 MW-like hosts and 10,579 LSBG candidates associated with them. 
However, there are still a significant fraction of spurious objects in this cross-matched LSBG sample, including galactic cirri, tidal tails/streams, shredded large galaxies, compact sources blended with galaxy outskirts, etc. As introduced in Section \ref{sec:deblending}, we perform a deblending step to effectively remove these spurious objects. There are 2,673 objects left after the deblending cuts. Next, we model them using the Spergel profile as described in Section \ref{sec:modeling} and obtain their properties from the fitting results. Based on the modeling results, we apply the same color cuts as in Section \ref{sec:deblending} and a size cut of $1.6\arcsec < r_e < 15\arcsec$ to further remove unreliable fits and false positives. We also remove duplicated objects. In the end, we have 2,510 LSBG candidates as our final LSBG sample, from which we construct the ultra-diffuse galaxy (UDG) sample and the ultra-puffy galaxy (UPG) samples as follows.

@@

The measured central surface brightness might be biased by nuclear star clusters \citep{Neumayer2020} or other contaminants. Therefore in this work, we use the average surface brightness within effective radius $\sbeff$ to define UDG. The difference between the average surface brightness and the central surface brightness for a \sersic{} profile can be analytically calculated, where $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1.124$ for $n=1$ and 0.796 for $n=0.8$ \citep{Graham2005,Yagi2016}. Since dwarf galaxies and UDGs typically show a range of \sersic{} index $0.8 < n < 1.2$ \citep{vanDokkum2015,ELVES-I}, we take $\overline{\mu}_{\mathrm{eff}} - \mu_0 = 1$ as an average value. In this work, we define UDGs to be galaxies with $r_e+\sigma(r_e) > 1.5$ kpc and $\sbeff + \sigma(\sbeff) > 25\ \sbunit$, which takes the measurement errors into account. This definition maximizes the consistency with the definition in \citet{vanDokkum2015} while not losing UDGs harboring nuclear star clusters.

@@

The concept of UDG was proposed for those dwarf galaxies with large physical size and diffuse light distribution. However, the size of a galaxy is strongly correlated with its mass, known as the mass-size relation \citep[e.g.,][]{Lange2015}. The slope of the mass-size relation has been shown to be color-dependent for galaxies above $M_\star > 10^{8.5}\ M_\odot$: blue star-forming galaxies have a shallower slope, whereas red quenched galaxies have a steeper slope. However, recent works show that the mass-size relation in the dwarf galaxy regime ($10^{5.5} < M_\star < 10^{8.5}$) is quite universal: the slope and intercept are not sensitive to the color and morphology of dwarf galaxy \citep{ELVES-I}. This gives us a chance to define a subset of dwarf galaxies that are outliers on the mass-size plane. Taking the measured mass-size relation from \citet{ELVES-I} $\log\, (r_e/\mathrm{pc}) = 0.247\, \log\, (M_\star/M_\odot) + 1.071$ and a scatter of $\sigma=0.181$ dex, we define a population of ultra-puffy galaxies (UPGs) to be galaxies that are $>1.5\sigma$ above the mass-size relation. The UPGs are not necessarily large in physical size or faint in average surface brightness, but they are outliers in size for their masses. Both UDG and UPG represent subsets of dwarf galaxies that are larger and more diffuse than average. However, the hard cut on size (1.5 kpc) means that the UDG definition excludes ``large'' galaxies at the low-mass end because as mass goes smaller, the average size also gets smaller. The surface brightness cut also biases the UDG sample because of mass-to-light ratio differences between blue and red galaxies, as will be discussed in Section \ref{sec:quench}. The definition of UPG based on the observed mass-size relation is more physically-motivated, and UPGs better represent a homogeneous subset of dwarf galaxies along the stellar mass axis. There is also no color preference in the UPG definition for a given stellar mass. It is worth noting that a definition based on the mass-size relation was already used in simulation studies where simulations cannot reproduce the observed mass-size relation \citep[e.g.,][]{Benavides2021}.

@@

\jiaxuan{vdb17 doesn't estimate measurement bias.}
